---
title: "TX2021_HR"
author: "Kaera Utusmi"
date: "June 15, 2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MASS)
library(vcd)
library(Hmisc)
library(adehabitatHR)
library(readxl)
library(rgdal)
library(move)
library(mapview)

setwd("C:/Users/Kaera/Documents/Research/Texas 2021")

TXHROBS <- read_excel("A_inornatusHR.xlsx")
```

###Calculate minimum convex polygons for adults. First we put the x and why coordinates in a matrix, then make a data frame from the observation numbers, the combine x and y as bundled coordinates. **The units produced are equivalent square meters.  Normally I would convert the x,y coordiinates to meters (instead of cm), but the relationship between m/ha and cm/m2 is the same.

```{r}
TXxy<-matrix(cbind(TXHROBS$x,TXHROBS$y), ncol=2)

TXsp<-data.frame(TXHROBS$id)
coordinates(TXsp)<-TXxy
TXmcp<-mcp.area(TXsp[,"TXHROBS.id"], percent=c(50,95,99), plotit=FALSE)
TXmcp<- as.data.frame(TXmcp)
TXmcp<- t(TXmcp)
head(TXmcp)

```

## #Homrange estimation using the kernal method  Two slightly different ways to get the hr calculated (see package vignette p 27) but they give basically the same values.


```{r}
TXud<-kernelUD(TXsp[,"TXHROBS.id"],h="href", grid=100, extent=1.5)
image(TXud)

ext<-extent(TXxy) # extent() returns the extent/dimensions of a raster or Spatial object
multiplyers <- c((ext[2]-ext[1])*0.3, (ext[4]-ext[3])*0.3) # (the max - min)*0.3
ext <- extend(ext, multiplyers) # extends the raster specified 1st, by the next specified object
grd <- raster(ext) #makes object into a raster
res(grd) <- 50 #sets the cell size to 50m
rm(multiplyers, ext) #removes the specified objects from the R memory
TXud<-kernelUD(TXsp[,"TXHROBS.id"],h="href",grid=as(grd,"SpatialPixels"), kern = "bivnorm")
#image(orud)    #vector is too large to visualize
aa<-kernel.area(TXud,percent=c(50,95))
aa<- t(aa)
aa

hrTXud<-getverticeshr(TXud)
hrTXud<- as.data.frame(hrTXud)

saveFile<- cbind(TXmcp, aa, hrTXud)
saveFile<- saveFile[c(-6)]
 
names<- c("MCP_50", "MCP_95", "MCP_99", "UD_50", "UD_95", "Total Area")
colnames(saveFile)<- names
write.csv(saveFile, file = "TXHR_Results.csv", col.names = T)
```
